New Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations

### 2020-01-03 nontex/install/windows/fn_installations.tex
VSCode with R and Linux Setup

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
]{article}

@@

@@

  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}

@@

% Use upquote if available, for straight quotes in verbatim environments

@@

\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}

@@

\@ifundefined{KOMAClassName}{% if non-KOMA class
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations},

@@

  filecolor=Maroon,

@@

  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs

@@

% Set default figure placement to htbp
\def\fps@figure{htbp}

@@

\title{New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R
(r-studio) and other Programs Installations}
\author{}
\date{\vspace{-2.5em}}

@@

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{where}\NormalTok{ anaconda}
\CommentTok{# C:/ProgramData/Anaconda3/Scripts/anaconda.exe}
\ExtensionTok{where}\NormalTok{ python}
\CommentTok{# C:/ProgramData/Anaconda3/python.exe}
\ExtensionTok{where}\NormalTok{ jupyter}
\CommentTok{# C:/ProgramData/Anaconda3/Scripts/jupyter.exe}
\ExtensionTok{where}\NormalTok{ jupyter-kernelspec}
\CommentTok{# if R installed already}
\ExtensionTok{where}\NormalTok{ r}

\CommentTok{###############################}
\CommentTok{# Add these to Windows PATH:}
\CommentTok{###############################}
\CommentTok{# C:/ProgramData/Anaconda3/Scripts}
\CommentTok{# C:/ProgramData/Anaconda3}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# # if there are bugs}
\CommentTok{# conda clean --packages}
\CommentTok{# use conda-forge as main channel, more updated packages}
\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
\CommentTok{# normal update}
\ExtensionTok{conda}\NormalTok{ update --all}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# windows}
\NormalTok{python }\StringTok{"C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"}
\NormalTok{python }\StringTok{"C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"}
\CommentTok{# linux}
\NormalTok{python }\OperatorTok{~}\ErrorTok{/}\NormalTok{PyFan}\OperatorTok{/}\NormalTok{ProjectSupport}\OperatorTok{/}\NormalTok{Testing}\OperatorTok{/}\NormalTok{Numpy}\OperatorTok{/}\NormalTok{Functions.py}
\NormalTok{python }\OperatorTok{~}\ErrorTok{/}\NormalTok{PyFan}\OperatorTok{/}\NormalTok{ProjectSupport}\OperatorTok{/}\NormalTok{graph}\OperatorTok{/}\NormalTok{subplot.py}
\end{Highlighting}
\end{Shaded}

\hypertarget{additional-packages}{%
\subsection{Additional Packages}\label{additional-packages}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{conda install statsmodels datashape seaborn}
\CommentTok{# conda install statsmodels}
\CommentTok{# conda install datashape}
\CommentTok{# conda install seaborn}

\NormalTok{conda install }\OperatorTok{-}\NormalTok{c conda}\OperatorTok{-}\NormalTok{forge interpolation awscli}
\CommentTok{# conda install -c conda-forge interpolation}
\CommentTok{# conda install -c conda-forge awscli}

\NormalTok{conda install }\OperatorTok{-}\NormalTok{c anaconda boto3}

\NormalTok{conda install }\OperatorTok{-}\NormalTok{c r r}\OperatorTok{-}\NormalTok{irkernel}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{fully-uninstall-r}{%
\subsection{Fully uninstall r}\label{fully-uninstall-r}}

open up RStudio, and see where paths are. also open up R from command
prompt, see where paths are.

@@

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://cloud.r-project.org/}{download R}
\item
  \href{https://rstudio.com/products/rstudio/download/}{download
  R-studio}
\item
  Open R-studio and auto-detect R
\item
  Install packages
\end{enumerate}

note that installation will not work if the machine's version of R is
not up to date, this could be the case with default R versions for some
linux installations.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Install R-tools}
\KeywordTok{install.packages}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\KeywordTok{install.Rtools}\NormalTok{()}
\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}bin;}
\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}mingw_32\textbackslash{}bin;}
\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}mingw_64\textbackslash{}bin;}

\CommentTok{# main packagevps}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidyr"}\NormalTok{, }\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{))}
\CommentTok{# development packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"irkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{))}
\CommentTok{# other packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Set up Channel}
\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
\CommentTok{# install key r packages within a r-environment}
\ExtensionTok{conda}\NormalTok{ env remove -n r_env}
\ExtensionTok{conda}\NormalTok{ create -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2}
\CommentTok{# see all installed environments}
\ExtensionTok{conda}\NormalTok{ env list}
\CommentTok{# activate an environment to use it, if in base, r does not exist, isolated in r_env}
\ExtensionTok{conda}\NormalTok{ activate r_env}
\CommentTok{# see packages in environment}
\ExtensionTok{conda}\NormalTok{ list}
\CommentTok{# to quit}
\ExtensionTok{conda}\NormalTok{ deactivate}
\end{Highlighting}
\end{Shaded}

@@

This did not work in windows, \emph{tidymodels} failed to install.
Perhaps because of directory issues. \emph{tidymodels} required
\emph{rstanarm}, and \emph{rstanarm} failed to install.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{### One line}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-aer r-minpack.lm r-knitr r-kableExtra r-matlab}
\CommentTok{# conda install -c conda-forge r-rstanarm}

\CommentTok{#######################################}
\CommentTok{### Estimation}
\CommentTok{#######################################}
\CommentTok{# Estimation Tools}
\CommentTok{# tidymodels does not work fron conda install}
\CommentTok{# Linear Regression Package}
\CommentTok{# https://anaconda.org/conda-forge/r-aer}
\CommentTok{# Nonlinear Regression Package}
\CommentTok{# https://anaconda.org/conda-forge/r-minpack.lm}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-aer r-minpack.lm}
\CommentTok{# enter r and use devtools}
\CommentTok{# install.packages("tidymodels")}

\CommentTok{#######################################}
\CommentTok{### Visualiation}
\CommentTok{#######################################}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-knitr r-kableExtra}

\CommentTok{#######################################}
\CommentTok{### Utilities}
\CommentTok{#######################################}
\CommentTok{# Allowing for Invoking Matlab Files from Inside R}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-matlab}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\OperatorTok{<}\NormalTok{!}\ExtensionTok{--}\NormalTok{ for ubuntu --}\OperatorTok{>}
\FunctionTok{wget} \StringTok{"https://download1.rstudio.org/desktop/bionic/amd64/rstudio-1.2.5033-amd64.deb"}
\FunctionTok{sudo}\NormalTok{ apt install ./rstudio-1.2.5033-amd64.deb}
\OperatorTok{<}\NormalTok{!}\ExtensionTok{--}\NormalTok{ for debian --}\OperatorTok{>}
\FunctionTok{wget} \StringTok{"https://download1.rstudio.org/desktop/debian9/x86_64/rstudio-1.2.5033-amd64.deb"}
\FunctionTok{sudo}\NormalTok{ apt install ./rstudio-1.2.5033-amd64.deb}
\ExtensionTok{conda}\NormalTok{ install -c r rstudio}
\BuiltInTok{cd} \StringTok{"C:/Program Files/RStudio/bin"}
\ExtensionTok{rstudio.exe}

@@

@@

\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}summarize\textbackslash{}dist\textbackslash{}fst_hist_onevar.Rmd}
\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}support\textbackslash{}tibble\textbackslash{}fs_tib_basics.Rmd}
\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}optimization\textbackslash{}cesloglin\textbackslash{}fst_ces_plan_linlog.Rmd}
\end{Highlighting}
\end{Shaded}

@@

  \begin{itemize}
  \tightlist
  \item
    these folders, once various packages are installed, could be very
    large, many GB
  \end{itemize}
\item
  latex packages from distributions
\item
  editor (gui): Atom, texStudio, etc
\end{enumerate}

@@

\hypertarget{compile-in-atom}{%
\subsection{Compile in Atom}\label{compile-in-atom}}

Install the \href{https://github.com/thomasjo/atom-latex}{latex} package
on atom.

>>>>

\documentclass[]{article}

@@

\usepackage{fixltx2e} % provides \textsubscript

@@

\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}

@@

  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
% use upquote if available, for straight quotes in verbatim environments

@@

% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}

@@

\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={New Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations},

@@

@@

            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\setlength{\parskip}{6pt plus 2pt minus 1pt}
}

@@

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{New Computer Data-Science Set-up: Python (anaconda, pycharm), R
(r-studio) and other Programs Installations}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

@@

\hypertarget{objective}{%
\section{Objective}\label{objective}}

For the following types of programming tasks, install relevant programs,
that are cross platform compatible. Test at the end that example
programs work.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Python

  \begin{itemize}
  \tightlist
  \item
    Anaconda Dist
  \item
    Pycharm
  \item
    atom hydrogen
  \end{itemize}
\item
  R

  \begin{itemize}
  \tightlist
  \item
    R
  \item
    Rstudio
  \item
    atom hydrogen
  \end{itemize}
\item
  Matlab

  \begin{itemize}
  \tightlist
  \item
    Matlab
  \end{itemize}
\item
  Latex and PDF

  \begin{itemize}
  \tightlist
  \item
    atom latex
  \item
    texstudio
  \item
    texlive
  \item
    okular pdf
  \end{itemize}
\end{enumerate}

Test at the end:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Do sample \emph{py} files work?

  \begin{itemize}
  \tightlist
  \item
    work from command line?
  \item
    work from atom (hydrogen)
  \end{itemize}
\item
  Do sample \emph{rmd} files work?

  \begin{itemize}
  \tightlist
  \item
    work from r-studio
  \item
    work from atom (hydrogen), r file
  \end{itemize}
\item
  Do tex templates compile?

  \begin{itemize}
  \tightlist
  \item
    tikz files
  \item
    template files with bib
  \end{itemize}
\end{enumerate}

\emph{note}: Github people seem to have slowed down updating Atom since
microsoft acquisition

@@

To install conda in Debian, follow
\href{https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html}{these
instructions}.

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# To remove conda Fully}
\FunctionTok{rm}\NormalTok{ -rf ~/anaconda3}

\ExtensionTok{where}\NormalTok{ anaconda}
\CommentTok{# C:/ProgramData/Anaconda3/Scripts/anaconda.exe}
\ExtensionTok{where}\NormalTok{ python}
\CommentTok{# C:/ProgramData/Anaconda3/python.exe}
\ExtensionTok{where}\NormalTok{ jupyter}
\CommentTok{# C:/ProgramData/Anaconda3/Scripts/jupyter.exe}
\ExtensionTok{where}\NormalTok{ jupyter-kernelspec}
\CommentTok{# if R installed already}
\ExtensionTok{where}\NormalTok{ r}

\CommentTok{###############################}
\CommentTok{# Add these to Windows PATH:}
\CommentTok{###############################}
\CommentTok{# C:\textbackslash{}ProgramData\textbackslash{}Anaconda3\textbackslash{}Scripts}
\CommentTok{# C:\textbackslash{}ProgramData\textbackslash{}Anaconda3}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# if there are bugs}
\CommentTok{# conda clean --packages}
\CommentTok{# use conda-forge as main channel, more updated packages}
\ExtensionTok{conda}\NormalTok{ config --get channels}
\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
\ExtensionTok{conda}\NormalTok{ config --get channels}
\CommentTok{# remove conda-forge from channels (do so for main env install)}
\ExtensionTok{conda}\NormalTok{ config --remove channels conda-forge}
\CommentTok{# normal update}
\ExtensionTok{conda}\NormalTok{ update --all}

\CommentTok{# install additional packages}
\ExtensionTok{conda}\NormalTok{ install -y statsmodels datashape seaborn}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge -y interpolation awscli}
\ExtensionTok{conda}\NormalTok{ install -c anaconda -y boto3}
\end{Highlighting}
\end{Shaded}

@@

Fist test python under command line:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# windows}
\ExtensionTok{python} \StringTok{"C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"}
\ExtensionTok{python} \StringTok{"C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"}
\CommentTok{# linux}
\ExtensionTok{python}\NormalTok{ ~/PyFan/ProjectSupport/Testing/Numpy/Functions.py}
\ExtensionTok{python}\NormalTok{ ~/PyFan/ProjectSupport/graph/subplot.py}
\end{Highlighting}
\end{Shaded}

\hypertarget{jupyter-and-atom-hydrogen}{%
\subsection{Jupyter and Atom Hydrogen}\label{jupyter-and-atom-hydrogen}}

For both Jupyter as well as Atom, always open from command prompt, open
from \emph{Anaconda Prompt} with admin rights.

First, open up \emph{Jupyter Notebook}, does the python kernel work? If
does not, uninstall and re-install Anaconda.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# start jupyter lab, from prompt}
\ExtensionTok{jupyter}\NormalTok{ lab}
\end{Highlighting}
\end{Shaded}

Now test python within atom:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  install hydrogen in atom. Follow
  \href{http://nteract.io/atom}{instructions}.

  \begin{itemize}
  \tightlist
  \item
    terminal in windows or linux after installation: \emph{apm install
    hydrogen}
  \item
    apm is the atom package manager.
  \end{itemize}
\item
  Pull/Sync with Git and open mulitple projects in atom, follow
  \href{https://fanwangecon.github.io/Tex4Econ/nontex/install/git/fs_git_setup.html}{guide
  here}.
\item
  go to the programs above and try to run.
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Once atom is installed, can use apm to install packages}
\FunctionTok{apm}\NormalTok{ install hydrogen}
\FunctionTok{apm}\NormalTok{ install project-manager}
\FunctionTok{apm}\NormalTok{ install sublime-style-column-selection}
\FunctionTok{apm}\NormalTok{ install minimap}

\CommentTok{# vim distraction free editing}
\FunctionTok{apm}\NormalTok{ install vim-mode-plus}
\FunctionTok{apm}\NormalTok{ install zen}

\CommentTok{# Inside Conda open up atom}
\ExtensionTok{atom}

\CommentTok{# open multiple projects from atom at the same time, after repos synced}
\ExtensionTok{atom}\NormalTok{ ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ}
\CommentTok{# open up any py from from within, try 1+1, does it work?}
\CommentTok{# also use script, try ctrl + shift + b, run whole file (not hydrogen)}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{fully-uninstall-r}{%
\subsection{Fully Uninstall r}\label{fully-uninstall-r}}

Open up RStudio, and see where paths are. also open up R from command
prompt, see where paths are.

@@

For Linux:

\begin{itemize}
\tightlist
\item
  if used apt-get to install, R installed under main user drive,
  deactivate conda, and check which conda
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Exit Conda}
\ExtensionTok{conda}\NormalTok{ deactivate}
\CommentTok{# where is R installed outside of Conda}
\FunctionTok{which}\NormalTok{ R}
\CommentTok{# /usr/bin/R}
\CommentTok{# To remove all}
\FunctionTok{sudo}\NormalTok{ apt-get remove r-base}
\FunctionTok{sudo}\NormalTok{ apt-get remove r-base-core}

\CommentTok{# Inside Conda base}
\ExtensionTok{conda}\NormalTok{ activate}
\CommentTok{# Conda r_env}
\ExtensionTok{conda}\NormalTok{ activate r_env}
\CommentTok{# Where is it installed?}
\FunctionTok{which}\NormalTok{ R}
\CommentTok{# /home/wangfanbsg75/anaconda3/bin/R}
\ExtensionTok{conda}\NormalTok{ uninstall r-base}
\end{Highlighting}
\end{Shaded}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://cloud.r-project.org/}{download R}

  \begin{itemize}
  \tightlist
  \item
    for debian:
    \href{https://cran.r-project.org/bin/linux/debian/}{Johannes Ranke}
  \end{itemize}
\item
  \href{https://rstudio.com/products/rstudio/download/}{download
  R-studio}
\item
  Open R-studio and auto-detect R
\item
  Install packages
\end{enumerate}

note that installation will not work if the machine's version of R is
not up to date, this could be the case with default R versions for some
linux installations. For Debian for example, need to update the
\emph{source.list} to include sources that have more recent versions of
R.

Additionally, need to install \emph{libcurl4-openssl-dev} and
\emph{libssl-dev} from command prompt first inside Debian.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# If inside Debian, due to some tidymodel install issues, do this`}
\ExtensionTok{conda}\NormalTok{ install -c r r}
\ExtensionTok{conda}\NormalTok{ install -c r r-essentials}
\ExtensionTok{conda}\NormalTok{ install -c r r-igraph}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge igraph}

\CommentTok{# Go to get latesdebian latest r sources.list}
\FunctionTok{cat}\NormalTok{ /etc/apt/sources.list}
\CommentTok{# Install this First (should already be installed)}
\FunctionTok{sudo}\NormalTok{ apt install dirmngr}

\CommentTok{# Debian R is maintained by Johannes Ranke, copied from https://cran.r-project.org/bin/linux/debian/:}
\ExtensionTok{apt-key}\NormalTok{ adv --keyserver keys.gnupg.net --recv-key }\StringTok{'E19F5F87128899B192B1A2C2AD5F960A256A04AF'}
\CommentTok{# Add to source.list, for debian stretch (9)}
\CommentTok{# sudo su added for security issue as super-user}
\FunctionTok{sudo}\NormalTok{ su -c }\StringTok{"sudo echo 'deb http://cloud.r-project.org/bin/linux/debian stretch-cran35/' >> /etc/apt/sources.list"}
\CommentTok{# if added wrong lines, delete 3rd line}
\FunctionTok{sudo}\NormalTok{ sed }\StringTok{'3d'}\NormalTok{ /etc/apt/sources.list}

\CommentTok{# Update and Install R, should say updated from cloud.r}
\FunctionTok{sudo}\NormalTok{ apt-get update}
\FunctionTok{sudo}\NormalTok{ apt-get install r-base r-base-dev}

\CommentTok{# Also install these, otherwise r-packages do not install}
\CommentTok{# libxml2 seems need for tidymodels}
\FunctionTok{sudo}\NormalTok{ apt-get install libcurl4-openssl-dev}
\FunctionTok{sudo}\NormalTok{ apt-get install libssl-dev}
\FunctionTok{sudo}\NormalTok{ apt-get install libxml2-dev}
\end{Highlighting}
\end{Shaded}

Which R?

\begin{itemize}
\tightlist
\item
  \emph{export RSTUDIO\_WHICH\_R=/usr/bin/R}
\item
  \emph{export RSTUDIO\_WHICH\_R=/home/wangfanbsg75/anaconda3/bin/R}
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Can enter R from Command Prompt Conda ENV, much faster than from r-studio}
\CommentTok{# Install R-tools, RTOOLS is for WINDOWS}
\KeywordTok{install.packages}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\KeywordTok{install.Rtools}\NormalTok{()}
\CommentTok{# c:/Rtools/bin;}
\CommentTok{# c:/Rtools/mingw_32/bin;}
\CommentTok{# c:/Rtools/mingw_64/bin;}

\CommentTok{# main packagevps}
\CommentTok{# tidymodel installation on linux difficult}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{, }\StringTok{"tidyr"}\NormalTok{))}
\CommentTok{# development packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"IRkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{))}
\CommentTok{# other packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}

\CommentTok{# Install my package, need to prepare package to work for ubuntu}
\CommentTok{# if install does not work, load locally}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}

\CommentTok{# Kernel}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
\NormalTok{IRkernel}\OperatorTok{::}\KeywordTok{installspec}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# outside of conda, install some depencies}
\FunctionTok{sudo}\NormalTok{ apt-get install libcurl4-openssl-dev}
\FunctionTok{sudo}\NormalTok{ apt-get install libssl-dev}
\FunctionTok{sudo}\NormalTok{ apt-get install libxml2-dev}

\CommentTok{# install key r packages within a r-environment}
\ExtensionTok{conda}\NormalTok{ env remove -n r_env}
\CommentTok{# start empty environment}
\ExtensionTok{conda}\NormalTok{ create -n r_env}
\CommentTok{# activate env and check, nothing yet}
\ExtensionTok{conda}\NormalTok{ activate r_env}
\ExtensionTok{conda}\NormalTok{ list}

\CommentTok{# check channel and add env specific channel}
\ExtensionTok{conda}\NormalTok{ config --get channels}
\CommentTok{# to get latest r, use conda-forge, which has more recent Rs}
\CommentTok{# conda config --env --add channels conda-forge}
\CommentTok{# channels for base}
\ExtensionTok{conda}\NormalTok{ config --get channels}
\CommentTok{# channels for cur env}
\ExtensionTok{conda}\NormalTok{ config --get channels --env}

\CommentTok{# install files}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y}

\CommentTok{# trouble with igraph installation, install here from conda}
\CommentTok{# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-igraph}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c conda-forge igraph}
\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-rstantools r-rstan r-rstanarm -y}

\CommentTok{# see all installed environments}
\ExtensionTok{conda}\NormalTok{ env list}
\CommentTok{# activate an environment to use it, if in base, r does not exist, isolated in r_env}
\ExtensionTok{conda}\NormalTok{ activate r_env}
\CommentTok{# see packages in environment}
\ExtensionTok{conda}\NormalTok{ list}
\CommentTok{# to quit}
\ExtensionTok{conda}\NormalTok{ deactivate}
\end{Highlighting}
\end{Shaded}

@@

\emph{tidymodel} has installation issues sometimes.

In \emph{r\_env}, type in \emph{R}, and then install from inside
terminal's R:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# enter into env}
\ExtensionTok{conda}\NormalTok{ activate r_env}
\CommentTok{# enter R or type in rstudio}
\CommentTok{# sicne R is only install inside r_env, has to enter rstudio from r_env}
\ExtensionTok{R}
\ExtensionTok{rstudio}

\CommentTok{# main packagevps}
\CommentTok{# tidymodel installation on linux difficult}
\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"rstantools"}\NormalTok{, }\StringTok{"rstan"}\NormalTok{, }\StringTok{"rstanarm"}\NormalTok{))}
\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"tidyr"}\NormalTok{, }\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{))}

\CommentTok{# tidymodels}
\CommentTok{# development packages}
\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"IRkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{))}
\CommentTok{# other packages}
\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}

\CommentTok{# Install my package, need to prepare package to work for ubuntu}
\CommentTok{# if install does not work, load locally}
\ExtensionTok{devtools}\NormalTok{::install_github(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}

\CommentTok{# Kernel}
\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
\FunctionTok{IRkernel::installspec()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\OperatorTok{<}\NormalTok{!}\ExtensionTok{--}\NormalTok{ for ubuntu --}\OperatorTok{>}
\FunctionTok{wget} \StringTok{"https://download1.rstudio.org/desktop/bionic/amd64/rstudio-1.2.5033-amd64.deb"}
\OperatorTok{<}\NormalTok{!}\ExtensionTok{--}\NormalTok{ for debian --}\OperatorTok{>}
\FunctionTok{sudo}\NormalTok{ apt install ./rstudio-1.2.5033-amd64.deb}
\FunctionTok{wget} \StringTok{"https://download1.rstudio.org/desktop/debian9/x86_64/rstudio-1.2.5033-amd64.deb"}
\FunctionTok{sudo}\NormalTok{ apt install ./rstudio-1.2.5033-amd64.deb}
\ExtensionTok{conda}\NormalTok{ install -c r rstudio}
\BuiltInTok{cd} \StringTok{"C:/Program Files/RStudio/bin"}
\ExtensionTok{rstudio.exe}

@@

\CommentTok{# for r-kernel to work in Atom}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{'IRkernel/IRkernel'}\NormalTok{)}
\NormalTok{IRkernel}\OperatorTok{::}\KeywordTok{installspec}\NormalTok{()}

@@

\CommentTok{# C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.Rmd}
\CommentTok{# C:/Users/fan/R4Econ/support/tibble/fs_tib_basics.Rmd}
\CommentTok{# C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.Rmd}
\end{Highlighting}
\end{Shaded}

@@

  \begin{itemize}
  \tightlist
  \item
    these folders, once various packages are installed, could be very
    large, many GB
  \end{itemize}
\item
  latex packages from distributions
\item
  editor (gui): Atom, Sublime text, texStudio, etc
\end{enumerate}

@@

\hypertarget{compile-in-atom-and-texstudio}{%
\subsection{Compile in Atom and
Texstudio}\label{compile-in-atom-and-texstudio}}

Install the following two packages in atom:
